Anisotropic in-plane thermal conductivity observed in multilayer silicene

### 2017-06-28 latex/paper.tex
Update paper.tex

considering only the relaxation time approxmition(RTA). We then use iterative method to consider in cross influence of the phonon exitatioin, witch alway give lager lifetime compare to RTA and more close to the real value.

the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The values are averaged for frequency bins to reduce complexity. The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation. The result is also consist with the trends of thermal conductivity.

@@

The anisotroy of phonon lifetime is due to the anisotropy of anharmonic effect. The Gruneisen parameters which represent the degree of anharmonic effect is also shown in FIG.\ref{fig:gruneisen}.
The larger the anharmonic effect the smaller the scattering lifetime of the phonons.

>>>>

considering only the relaxation time approxmition(RTA). We then use iterative method to consider in cross influence of the phonon exitatioin, witch always give lager lifetime compare to RTA and more close to the real value.

the phonon lifetime calculated with ShengBTE\cite{Li2014} are shown in FIG.\ref{fig:tau}. The values are averaged for frequency bins to reduce complexity. The lifetime of 3l2,4l1,5l1,6l1 along zigzag direction is larger while that of 2l1,2lh,3l1 has reverse relation. The result is also consist with the trends of thermal conductivity. The low frequency acoustic phonons exhibit much larger lifetime, indicating they contribute large part of thermal conducitivity. The relation between acoustic phonon lifetime and frequency could be expressed as $\tau\=k \omega^{-2}$ and diverge when omega tends to zero, witch is a common feature of low dimensional structures. The coefficient k for both direction are displayed in Table.3. The degree of divergence exhibit large anisotropy for the structures. However the difference of lifetime is pretty small when frequency is relatively high. So the anisotropy of low frequency phonon contribute the main part of anisotropy in phonon lifetime.

@@

The anisotropy of phonon lifetime is due to the anisotropy of anharmonic effect. To quatitily check the anharmonic effect we calculate the Gruneisen parameters with

\begin{equation}

\end{equation}

where V is the volumn of the unicell and $\omega$ is the phonon frequency. The shift of $\omega$ with V is due to the divirience from paraodic potential which reprensents for the harmonic situation. When the potenial is harmonic , all the Gruneisen parameters will vanish.
The Gruneisen parameters of all the structures are shown in FIG.\ref{fig:gruneisen}. The larger the anharmonic effect the smaller the scattering lifetime of the phonons. The most anharmonic phonons exist in the low frequency region and consist with previous result of phonon lifetime. The large difference between zigzag value and armchair could explain the anisotropy of phonon scattering.

To obtain a clear connection between  the surface characteristic we also statistic the force constants of different position of the structures.
